\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc} % Added for better font encoding and hyphenation
\usepackage{lmodern}     % Added for a modern font that supports more glyphs

% \input{glyphtounicode} % Usually not needed with hyperref and T1 fontenc
% \pdfgentounicode=1     % Usually not needed with hyperref and T1 fontenc

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small #3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{ % Ensure this has two arguments
\item
\begin{tabularx}{\textwidth}{X r}
\small #1 & \small #2 \\ % Added \small to #2 for consistency if it's used for dates
\end{tabularx}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Shivansh Kalra} \ \vspace{1pt}
\small +91-9717094960 
~|~ % Replaced ∣ with ~|~
 \href{https://linkedin.com/in/shivansh-kalra}{\underline{linkedin.com/in/shivansh-kalra}} 
~|~ % Replaced ∣ with ~|~
\href{https://github.com/shivansh193}{\underline{github.com/shivansh193}}
\end{center}

\section*{Summary}
\vspace{-5pt}
\small{Aspiring Product Manager with a strong Full Stack Development foundation (React.js, Node.js, MongoDB) and a passion for building user-centric, scalable SaaS platforms. Proven ability to identify user needs, translate them into technical solutions, and drive product development in fast-paced startup environments. Eager to leverage technical expertise, analytical skills, and a data-informed approach to contribute to impactful product strategies and roadmaps.}
\vspace{4pt}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Shiv Nadar University}{Noida, India}
{Bachelor of Technology in Computer Science}{Aug. 2023 -- Present}
\resumeSubheading
{Amity International School}{Gurgaon, India}
{High School Diploma, PCM Major}{May 2020 -- June 2022}
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Full Stack Development}{: React.js, Node.js, Express.js (Proficient), MongoDB, MERN Stack, TypeScript (Advanced), JavaScript (ES6+), HTML5, CSS3} \\
\textbf{Backend \& APIs}{: RESTful APIs, Python (Flask), Service-Oriented Architecture, SQL (PostgreSQL), Firebase (NoSQL)} \\ % Escaped &
\textbf{Frontend Technologies}{: State Management (Redux, Context API), Navigation (React Navigation), Animations (Reanimated), Responsive Design} \\
\textbf{Product \& Strategy}{: User Research, Market Analysis (Basic), A/B Testing (Conceptual), Roadmapping, Agile/Scrum, Prototyping, Wireframing (Figma), Competitive Analysis, Data Analysis, User Story Creation, Backlog Grooming} \\ % Escaped &
\textbf{Tools \& DevOps}{: Git, Jira, Figma, Postman, Docker (Familiarity), CI/CD Practices (Vercel), Agile Methodologies} \\ % Escaped &
\textbf{Concepts}{: Object-Oriented Design, Clean Code, Data Structures \& Algorithms, Scalable Systems, Problem Solving, Startup Mindset (Ship Fast, Iterate Faster), User-Centric Design} % Escaped &
}}
\end{itemize}

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\href{https://product-roadmap-beta.vercel.app}{\textbf{BuildFlow}} 
~|~ % Replaced ∣
 \emph{React, TypeScript, Next.js, Vercel, API Integration, CSS}}{}
\resumeItemListStart
\resumeItem{Identified a market need for accessible project roadmap tools, leading to the design, development, and launch of a full-stack SaaS web application.}
\resumeItem{Defined core product features based on potential user workflows, enabling users to create, manage, and share roadmaps; attracted 200+ active users and 500+ roadmaps in 2 months.}
\resumeItem{Iteratively improved UI/UX based on user feedback and engagement metrics, ensuring cross-device compatibility and intuitive navigation; deployed on Vercel with CI/CD.}
\resumeItemListEnd

\resumeProjectHeading
  {\href{https://catalystiqplat.vercel.app}{\textbf{CatalystIQ Hub}} ~|~ \emph{React, TypeScript, Python (Flask), REST APIs, Figma}}{} % Replaced ∣
  \resumeItemListStart
    \resumeItem{Conceptualized and engineered a hiring platform to streamline recruitment, translating user needs identified from market gaps and Figma designs into a functional UX.}
    \resumeItem{Defined data models and API specifications (Python/Flask backend) to support core platform features, resulting in a system aimed at improving hiring decision efficiency by 20\%.}
    \resumeItem{Prioritized development of reusable UI components (TypeScript) to ensure product scalability and maintainability, focusing on a robust user experience.}
  \resumeItemListEnd
  
\resumeProjectHeading
  {\href{https://catalystiq.fun}{\textbf{WEHIndia}} ~|~ \emph{Next.js (React), TypeScript, Firebase (NoSQL), CSS}}{} % Replaced ∣
  \resumeItemListStart
    \resumeItem{Contributed to an event-vendor matching platform by developing key frontend features, addressing user needs for responsive UI and real-time data synchronization with Firebase.}
    \resumeItem{Implemented complex UI components and state management, focusing on enhancing user interaction with dynamic data and ensuring type safety for platform stability.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{DeBi} ~|~ \emph{Solidity, Hardhat, Ethers.js (JavaScript), Blockchain}}{} % Replaced ∣
  \resumeItemListStart
    \resumeItem{Explored decentralized solutions for fundraising by developing a platform using Solidity and Ethers.js, defining core functionalities and smart contract logic to address transparency needs.}
    \resumeItem{Demonstrated understanding of blockchain's potential for novel product applications by building a full-stack (JavaScript for frontend) decentralized application.}
  \resumeItemListEnd

 \resumeProjectHeading
  {\href{https://www.kaggle.com/code/pustak/chainedthought}{\textbf{ChainedThought}} ~|~ \emph{Python, API SDK, Problem Solving}}{} % Replaced ∣
  \resumeItemListStart
    \resumeItem{Applied advanced problem-solving techniques to analyze complex data processing tasks, leveraging Python and external APIs to develop innovative solutions.}
    \resumeItem{Showcased ability to quickly learn and integrate new technologies to extract insights and deliver practical outcomes from data challenges.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Testline}{Remote}
  {Product Management Intern}{Dec. 2024 -- Feb. 2025}
  \resumeItemListStart
    \resumeItem{Spearheaded the development of a new product feature from ideation to launch, utilizing user feedback and competitive analysis to achieve a 15\% increase in user retention.}
    \resumeItem{Analyzed user signup processes using AI-based clustering, identifying key friction points and contributing to an 11\% reduction in drop-off rates.}
    \resumeItem{Collaborated on 3 AI-focused internal marketing tools, successfully reaching over 3000 users and boosting platform engagement.}
  \resumeItemListEnd

\resumeSubheading
  {Frontrunner}{Remote}
  {Technical Product Development Intern}{May 2024 -- Aug. 2024}
  \resumeItemListStart
    \resumeItem{Drove a 40\% increase in monthly revenue by creating 5 new income streams and prototyping 2 AI-based product MVPs.}
    \resumeItem{Conducted user testing with 25+ founders, iterating on product improvements that significantly reduced customer churn.}
    \resumeItem{Accelerated product development cycles by 30\% and enhanced team communication by implementing agile methodologies.}
  \resumeItemListEnd
  
\resumeSubheading
  {\href{https://catalystiqplat.vercel.app}{CatalystIQ}}{Gurgaon, India}
  {Founder \& Product Lead}{Jan. 2024 -- April 2024}
  \resumeItemListStart
    \resumeItem{Built and launched an AI-powered business solutions platform, achieving an 18\% user conversion rate and reducing data processing time by 30\%.}
    \resumeItem{Generated over ₹1 Lakh in revenue by securing collaborations with 10+ FMCG companies, leading to a 15\% quarterly growth.}
    \resumeItem{Engineered a machine learning-based hiring system using bit-task assignments, reducing the typical hiring time by over 65\%.}
  \resumeItemListEnd

\resumeSubheading
  {\href{https://petner-plat.vercel.app}{Petner}}{Remote}
  {Founder \& Product Developer}{Apr. 2023 -- Dec. 2023}
  \resumeItemListStart
    \resumeItem{Scaled a pet-care platform using AI recommendations, securing partnerships with 25+ local businesses and onboarding 100+ users to a successful pilot program.}
    \resumeItem{Led the end-to-end product lifecycle, from ideation and full-stack development (React Native, Firebase) to real-world prototype validation.}
    \resumeItem{Managed the full-stack architecture and integrated real-time data pipelines to improve service matching and user experience.}
  \resumeItemListEnd
  
\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart
\resumeItem{Top 100 Finalist - Google Gemini Hackathon (Demonstrated rapid ideation, learning, and application of new APIs to build functional prototypes solving defined problems)}
\resumeItem{ETHIndia 2023 Top 100 Project (Showcased ability to innovate, define a problem, and rapidly prototype user-focused solutions under pressure)}
\resumeItem{Solana HackerHouse Top 10 Projects (Further evidence of problem-solving, solution development, and product pitching)}
\resumeItem{IITB Eureka 2022 SemiFinalist (Recognized for entrepreneurial concept, market viability assessment, and early-stage product definition)}
\resumeSubHeadingListEnd
\end{document}